Percolation Analysis – Building a Package

### 2019-07-31 paper.Rmd
changed create_nodes to take input in function

@@

source("R/create_nodes_list_d.v4.7.R")
percolateNodes()

>>>>

# create df from input data set
data <- read.csv("source_data/BefundesNL-minimal.csv", sep = ",") #' crazy mistakes happen if this is wrong...
#' This file needs three columns: PlcIndex, Easting, Northing in this order.
#' Additional fields Lat Long not used for this program.
#' Note that the Easting and Northing need to be UK grid references with the Alphabetic
#'  grid square converted to a numeric prefix for each
#' List any entries with null values and write to file

@@

source("R/create_nodes_list_d.v4.7.R")
percolateNodes(data = data, radius_values = 10, limit = 500, radius_unit = 1)
